### 2019-11-13 cvpr_submission/related_work.tex

Another research focus area has been multimodal fusion and
attention for VQA. For multimodal fusion, earlier methods used concatenation or element-wise multiplication between multimodal
features \cite{zhou2015simple, antol2015}. Others proposed more sophisticated methods such as different approximated bilinear pooling methods to effectively integrate the multimodal features with second-order feature interactions \cite{fukui2016multimodal, kim2016hadamard}. Attention  research in VQA has demonstrated that learning question-guided visual attention on image regions is the most promising approach \cite{yang2016stacked, chen2015abc, ilievski2016focused}. Compositional reasoning tasks such as the CLEVR dataset, also benefit from multi-hop attention and reasoning methods \cite{hudson2018compositional, song2018explore}. Visualization of attention steps also provide interpretability, which is an increasingly important aspect. The MAC model \cite{hudson2018compositional} is a great example of such an approach. The follow-on model by the same authors~\cite{hudson2019learning}, called Neural State Machine (NSM) takes a slightly different approach and reason over graph structures rather than directly over spatial maps of visual features. Representing objects in a scene and their relationship as a graph is an obvious choice, which is another growing research direction \cite{haurilet2019s, teney2017graph, kim2018dynamic}.

Video Question Answering, aside from spatial queries, also focuses on questions that require \emph{temporal} reasoning. Early works \cite{mun2017marioqa, xu2017video, yu2017end} used LSTMs to encode video frames and text queries to leverage temporal attention to selectively attend to essential frames in a video. These approaches might be sufficient for action-recognition type of tasks but fall short when spatio-temporal reasoning is required. Learning long-term dependencies is also another challenge that LSTMs may struggle with. Yin et al. \cite{yin2019memory} recently proposed a memory-augmented neural network (MANN) architecture for video QA which leverages the external memory for storing and retrieving useful information in questions and videos and modeling the long-term visual-textual dependence.
Our work is mostly related to the MAC and MANN type models. An important distinction of our approach is the frame-by-frame processing of the video input. Prior studies typically divide the whole video into clips; e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by an aggregation over clips to form a single video representation.
Nevertheless, when reasoning and producing the answer, the system has \emph{access to all frames}. Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history. However, in real-time dialog or video monitoring, it is not always possible to keep the entire history of conversation nor all frames from the beginning of the recording.

>>>>

Another research focus area has been multimodal fusion and
attention for VQA. For multimodal fusion, earlier methods used concatenation or element-wise multiplication between multimodal
features \cite{zhou2015simple, antol2015}.  Others proposed more sophisticated methods such as different approximated bilinear pooling methods to effectively integrate the multimodal features with second-order feature interactions \cite{fukui2016multimodal, kim2016hadamard, kim2016hadamard} .  Attention  research in VQA have demonstrated that learning question-guided visual attention on image regions is the most promising approach \cite{yang2016stacked, chen2015abc, ilievski2016focused}.   Compositional reasoning tasks such as the CLEVR dataset, also benefit from multi-hop attention and reasoning methods \cite{hudson2018compositional, song2018explore}.   Visualization of attention steps also provide interpretability, which is an increasingly important aspect. The MAC model \cite{hudson2018compositional} is a great example of such an approach.  The follow-on model by the same authors  \cite{hudson2019learning}, called Neural State Machine (NSM) takes a slightly different approach and reason over graph structures rather than directly over spatial maps of visual features.  Representing objects in a scene and their relationship as a graph is an obvious choice, which is another growing research direction \cite{haurilet2019s, teney2017graph, kim2018dynamic}.

Video question answering, aside from spatial queries, also focuses on questions that require temporal reasoning .  Early works \cite{mun2017marioqa, xu2017video, yu2017end} used LSTMs to encode video frames and text to leverage temporal attention to attend to essential frames in a video selectively.   These approaches might be sufficient for action-recognition types of tasks but fall short when spatio-temporal reasoning is required.  Learning long-term dependencies is also another challenge that LSTMs may struggle with.  Yin et al. 2019 \cite{yin2019memory} recently proposed a memory-augmented neural network (MANN) architecture for video QA which leverages the external memory for storing and retrieving useful information in questions and videos and modeling the long-term visual-textual dependence.
Our work is mostly related to the MAC and MANN type models. An important distinction of our approach is the frame-by-frame processing of the video input.  Prior studies typically divide the whole video into clips; e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over clips to form a single video representation.
Nevertheless, when reasoning and producing the answer, the system has \textit{access to all frames}.  Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history. However, in real-time dialog or video monitoring, it is not always possible to keep the entire history of conversation nor all frames from the beginning of the recording.
